RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R

### 2014-06-24 manuscripts/manuscript.Rmd
added the use case of interacting with NeXML-based web services

      4. RNeXML is well suited for users to preserve and maintain their
      personal archives of phylogenetic and comparative trait data in consistent,
      query-able, and cross-platform format, or leverage the rapidly growing 
      public community archives of rich NeXML files.

>>>>

      4. RNeXML is well suited for users to preserve and maintain their
      personal archives of phylogenetic and comparative trait data in consistent,
      query-able, and cross-platform format, to leverage the rapidly growing 
      public community archives of rich NeXML files, and to interact with web
      services that deliver their results (with their provenance) as NeXML.
